Mode and tempo of promoter evolution in the \textit{Paramecium aurelia} species complex

### 2019-03-08 manuscript.tex
Wrote beginnings of introduction.

\title{Mode and tempo of promoter evolution in the Paramecium aurelia species complex}

@@

%\datade{The POPRES data were obtained from dbGaP (accession no. phs000145.v1.p1).}

@@

\keyword{cis-regulatory regions, Paramecium, promoter evolution, TSS profiling.}

@@

Enter introduction here

>>>>

\title{Mode and tempo of promoter evolution in the \textit{Paramecium aurelia} species complex}

@@

@@

\keyword{cis-regulatory regions, duplicate genes, paralogous genes, Paramecium, promoter evolution, TSS profiling.}

@@

Genomic analysis across diverse eukaryotes has drawn attention to the important role of \textit{cis}-regulatory sequences in the evolution of gene expression \citep{Wittkopp:2008ki, Wittkopp:2011bc, Siepel:2014hd}. However, the \textit{cis}-regulatory sequence differences that accompany--or indeed underpin--species divergence remain largely unknown. A likely explanation for this is the difficulty in predicting \textit{cis}-regulatory regions from genomic sequence alone. Accurate estimation of promoter positions requires empirical, usually functional genomic evidence. At present, the best high-throughput approach to identify promoters at genome-scale is Transcription Start Site (TSS) profiling, which includes CAGE and RAMPAGE, among others. While TSS profiling methods differ methadologically, these methods capture the 5`-ends of capped mRNAs, sequence their corresponding cDNAs and align the reads to the genome to identify the TSSs present within a given transcriptome. Clustering of gene-adjacent TSSs defines a promoter, or transcription start region (TSR).
